---
title: "Exploratory Analysis"
author: "Amanda, August, Debbie, Jasmine, Rena"
date: "11/21/2021"
output: html_document
---

```{r setup, include=FALSE}
source("./summaryinfoscript.R")
source("./analysis1.R")
source("./analysis2.R")
source("./analysis3.R")
source("./map.R")
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```
<style type="text/css">
  body{
  font-size: 14pt;
}
</style>

## Summary Information  
Due to the school closures during COVID-19, over a billion children are at risk of falling behind in school. To keep students safe, countries have implemented virtual learning and we believe that this change has affected countless students. Our group wanted to explore this domain more, as we are all students pursuing higher education. We tried to look at the impacts of COVID-19 on the global education system to see if there were any national trends correlated with Covid-19.
  
- The total school enrollment in 2020 was **`r total_enrollment_in_2020`**.
- **`r highest_total_enrollment_year_2015to2020`** was the year from 2015 to 2020 with the highest total enrollment of students. 
- **`r highest_enrollment_country_in_2019`** had the highest school enrollment in 2019. 
- **`r highest_7_day_avg_cases_per_100k`** had the highest 7 day average of daily cases reported for children ages 12-15. 
- Austria's testing policy on 4/25/20 was **`r austria_testing_policy`**.


## Aggregate Table Script
#### Total Cases of COVID-19 from Colleges and Universities in Each State（updated on `r date`）
``` {r echo=FALSE}
College_cases_table
```
  
- The table shows the cases of COVID-19 from each state's colleges and universities, including every four-year public institution and every private college that competes in N.C.A.A. sports, by May 26, 2021.
- The variable "state_sum" is the total number of reported Covid-19 cases among university students and employees in all fields in each state since the beginning of the pandemic.
- Colleges and universities in **`r highest_state`** has the highest number of COVID cases since the beginning of the pandemic by May 26, 2021.
  
  
## Chart Scripts
### Chart 1

``` {r echo=FALSE}
closure_duration_plot
```

>The following chart show the top 20 countries with the longest school closure. We can see that the difference between one country and other are very significant. Even though the pandemic was global issue the action each country implemented was different.
  
### Chart 2

``` {r echo=FALSE}
vacc_trend_chart
```

>This chart is made from "COVID-19 Vaccination and Case Trends by Age Group, United States" dataset collected by CDC (Centers for Disease Control and Prevention). It shows the COVID-19 Vaccination Trends in 2021 in people aged from 12 to 24 in United States. The result chart reveals that there was a great increase of people accepting vaccination from April, but the total percentage till now is still very low and people who accepted one dose is about a time more than those who complete a whole serie. A surprising fact exposed by the chart is that, there are more people get vaccination from 12 to 17 group than those from 18 to 24.
  
### Chart 3

``` {r echo=FALSE}
daysofpolicies
```

>Here we see a pie chart depicting the top 10 countries with the highest level of Covid Testing policies (3), which means that tests are avaliable to everyone, whether they have symptoms or not. Each of these 10 countries has held this universal policy for the longest out of all countries.

### Chart 4
  
``` {r echo=FALSE}
cases_map
```

>The map above displays the Covid-19 cases in colleges and universities across the United States. The shades of color indicate the amount of cases in each state. As we can see that Texas has the darkest shade, this means it has the most amount of Covid cases in that specific state. States, such as American Samoa, Marshall Islands, and Northern Mariana Islands, are recorded to have none cases, have the lightest colors shown on the map. 
