---
title: "Exploratory Analysis"
author: "Amanda, August, Debbie, Jasmine, Rena"
date: "11/21/2021"
output: html_document
---

```{r setup, include=FALSE}
source("./summaryinfoscript.R")
source("./analysis2.R")
source("./school-closure.R")
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

## Summary Information

Due to the school closures during COVID-19, over a billion children are at risk of falling behind in school. To keep students safe, countries have implemented virtual learning and we believe that this change has affected countless students. Our group wanted to explore this domain more, as we are all students pursuing higher education. We tried to look at the impacts of COVID-19 on the global education system to see if there were any national trends correlated with Covid-19. 

The total school enrollment in 2020 was `r total_enrollment_in_2020`.`r highest_total_enrollment_year_2015to2020` was the year from 2015 to 2020 with the highest total enrollment of students. We found that `r highest_enrollment_country_in_2019` had the highest school enrollment in 2019. `r highest_7_day_avg_cases_per_100k` had the highest 7 day average of daily cases reported for children ages 12-15. Austria's testing policy on 4/25/20 was `r austria_testing_policy`.

``` {r echo=FALSE}
summary_table
```

A table of summary information is created above. 


## Including Plots
## School Closures
The following chart show the top 20 countries with the longest school closure. We can see that the difference between one country and other are very significant. Even though the pandemic was global issue the action each country implemented was different.

``` {r echo=FALSE}
closure_duration_plot
```


``` {r echo=FALSE}
vacc_trend_chart
```

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
